{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed, 300Hz

### 2017-04-23 draft.tex
Cleaned up the introduction a bit.

\begin{itemize}
\item Introduction: Should talk about, at least, motivation of this
  work, brief review of the literature, and contribution
\item Method: Detail the method w.r.t. a diagram of system
  architecture or pseudo code
\begin{itemize}
\item Kernelized Correlation Filter
\item A variant of KCF: Multiple KCF w/ PF ({\it E}nKCF, ${\it E}nKCF_{+RD}$
\item Re-detection for re-initialization: Modules for reliably
  detecting target-lost, for extensively searching the lost target,
  and for picking up the same target with a help from an appearance
  model or other models.
\begin{itemize}
\item To filter out unlikely box proposals,
\begin{itemize}
\item Use a prior information about box, our outputs, dimensions
  (e.g., a combination of width and height, aspect ratio, etc.)
\item Use the information about the trajectory of the target before we
  lose the target.
\end{itemize}
\item MTH: revisited
\item To make a box tighter, generate our own box proposals based on
  the locations of top $k$ box proposals from object proposal methods,
  e.g., Edge Box.
\end{itemize}
\end{itemize}
\item Experiment: Detail the data, and experimental setup; results and findings
\item Will compare the performance of {\it E}nKCF, Naive{\it E}nKCF,
  ${\it E}nKCF_{+RD}$ with those of the following tracking methods.
\begin{itemize}
\item vanilla-KCF w/ a fixed scale,
\item vanilla-KCF w/ three different scales,
\item LCT (Long-term Correlation Tracking) \cite{ma2015long}: Temporal
  correlation of a target over frames; a pyramid for different scales;
  re-detection w/ an appearance classifier (i.e., a naive Bayes w/
  random fern features in combination of sliding window). Temporal
  context regressor for translation over significant deformation and
  target regressor for scale variation.
\item MEEM (Multiple Experts using Entropy Minimization)
  \cite{zhang2014meem}.
\item SAMF (Scale Adaptive KCF)
\item STC (fast tracking via Spatio-Temporal Context learning)
  \cite{zhang2014fast}: 
\item Struck (Structured Output Tracking with Kernels)
\end{itemize}
\begin{itemize}
\item Visual tracker benchmark (VTB)
\item DTB-70: w/ and w/o motion estimation,
\item UAV123 \footnote{A set of images acquired from an UAV is called
  ``UAV123'' and publicly available from
  https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}
\item VOT
\end{itemize}
\item Conclusion
\end{itemize}

A recent proliferation of air/ground/water unmanned vehicle
technologies has ever increased interest on deployment of intelligent
algorithms on embedded or mobile platforms. Particularly, computer
vision algorithms are getting more attention primarily because those
platforms have limited payload to accommodate various sensors like
lidars or radars and installing a monocular camera even stereo rigs
would increase the usefulness of a mobile platform without increasing
much cost on it. For example, instead of being equipped with a bare
flight function with video recording, an unmanned air vehicle (UAV)
equipped with object or feature following would make it more useful in
the application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others. In this paper, we propose an object tracking algorithm
that aims at running on any embedded or mobile platforms. In
particular,

@@

For being a turnkey or ready-to-execute mission solution, an online
learning framework is more attractive. An object-following with a
self-supervised learning framework would work, but easy to fail to
serve a long-term solution.

One of the dominant frameworks for online object tracking based on the
correlation filter is to solve a regression problem in the frequency
domain. This framework assumes that the target information is given at
the very first image frame. Given this positive example for the
regression problem, a set of negative examples is mostly collected
around the initial, target bounding box and represented as a circulant
matrix \cite{henriques2015high}. One can optimally solve this
regression problem using a ridge regression in a closed form. However,
such a solution involves in expensive matrix operation
$\mathcal{O}(n^{3})$. The correlation filter provides one with a much
cheaper solution, $\mathcal{O}(n\log n)$ over element-wise
multiplication in a frequecny domain
\cite{bolme2010visual,henriques2015high}. Due to such a reformulation,
a complete pipeline of an object tracker based on the correlation
filter can be easily implemented and run in an online fashion with a
high speed. However, the vanilla form of such an online tracker is
prone to drift and fails to track a target over a long period of
time. This is explained well by the dilemma of stability-plasticity in
updating appearance model in that the appearance model will be
overfitted to only the images used to train and a compromise on the
frequency of updating the model is carefully implemented
\cite{santner2010prost}.

>>>>

\begin{comment}
\begin{itemize}
\item Introduction: Should talk about, at least, motivation of this
  work, brief review of the literature, and contribution
\item Method: Detail the method w.r.t. a diagram of system
  architecture or pseudo code
\begin{itemize}
\item Kernelized Correlation Filter
\item A variant of KCF: Multiple KCF w/ PF ({\it E}nKCF, ${\it E}nKCF_{+RD}$
\item Re-detection for re-initialization: Modules for reliably
  detecting target-lost, for extensively searching the lost target,
  and for picking up the same target with a help from an appearance
  model or other models.
\begin{itemize}
\item To filter out unlikely box proposals,
\begin{itemize}
\item Use a prior information about box, our outputs, dimensions
  (e.g., a combination of width and height, aspect ratio, etc.)
\item Use the information about the trajectory of the target before we
  lose the target.
\end{itemize}
\item MTH: revisited
\item To make a box tighter, generate our own box proposals based on
  the locations of top $k$ box proposals from object proposal methods,
  e.g., Edge Box.
\end{itemize}
\end{itemize}
\item Experiment: Detail the data, and experimental setup; results and findings
\item Will compare the performance of {\it E}nKCF, Naive{\it E}nKCF,
  ${\it E}nKCF_{+RD}$ with those of the following tracking methods.
\begin{itemize}
\item vanilla-KCF w/ a fixed scale,
\item vanilla-KCF w/ three different scales,
\item LCT (Long-term Correlation Tracking) \cite{ma2015long}: Temporal
  correlation of a target over frames; a pyramid for different scales;
  re-detection w/ an appearance classifier (i.e., a naive Bayes w/
  random fern features in combination of sliding window). Temporal
  context regressor for translation over significant deformation and
  target regressor for scale variation.
\item MEEM (Multiple Experts using Entropy Minimization)
  \cite{zhang2014meem}.
\item SAMF (Scale Adaptive KCF)
\item STC (fast tracking via Spatio-Temporal Context learning)
  \cite{zhang2014fast}: 
\item Struck (Structured Output Tracking with Kernels)
\end{itemize}
\begin{itemize}
\item Visual tracker benchmark (VTB)
\item DTB-70: w/ and w/o motion estimation,
\item UAV123 \footnote{A set of images acquired from an UAV is called
  ``UAV123'' and publicly available from
  https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}
\item VOT
\end{itemize}
\item Conclusion
\end{itemize}
\end{comment}

A recent proliferation of air/ground/water unmanned vehicle
technologies has ever increased interests on deployment of intelligent
algorithms on embedded or mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because those mobile platforms have limited payload to carry other
active sensors and, without increasing much cost, installation of a
monocular camera even stereo rigs would increase the usefulness of a
mobile platform. For example, instead of just bare flight function
with video recording, an unmanned air vehicle (UAV) equipped with
object or feature following would make it more useful in the
application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

In this paper, we propose a single-target tracking that aims at
running on any embedded or mobile platforms that doesn't require an
offline training, and can run on an embedded system. In particular, we
would like to make our algorithm 1) learn the appearance model of a
target on the fly and 2) run as fast on a typical desktop as up to
300Hz so that it could run up to 30Hz when it is deployed on a
low-end, embedded system. With these features, our tracking algorithm
is ready to track an object of interest when it is deployed on an
embedded system. To this end, an online object tracking is more
appropriate.

@@

One of the dominant frameworks for online object tracking is one based
on the correlation filter that essentially solves a regression problem
in the frequency domain. This framework assumes that the target
information is given at the very first image frame like other online
tracking algorithms. Given this positive example for the regression
problem, a set of negative examples is collected around the initial,
target bounding box and represented as a circulant matrix
\cite{henriques2015high}. One can optimally solve this regression
problem using a ridge regression in a closed form. However, such a
solution involves in expensive matrix operations
$\mathcal{O}(n^{3})$. The correlation filter provides one with a much
cheaper solution, $\mathcal{O}(n\log n)$ over element-wise
multiplication in a frequecny domain
\cite{bolme2010visual,henriques2015high}. Due to such a reformulation,
a complete pipeline of an object tracker based on the correlation
filter can be easily implemented and run in an online fashion
efficiently. However, the vanilla form of such an online tracker is
prone to drift, and fails to track a target over a long period of
time. This is explained well by the dilemma of stability-plasticity in
updating appearance model in that the appearance model will be
overfitted to only the images used to train and a compromise on the
frequency of updating the model is carefully implemented
\cite{santner2010prost}.
